Just algae 18S community comparison

### 2019-11-05 code/community_comparison_18s.Rmd
ran 18s snow algae assignments locally

```{r, include=F}
rel_abund <- read_csv(here("data/03_filtered/18s_algae/18s_algae.filtered_cleaned_rel_abund.csv"))
tree_18s <- read.tree(here("output/tree/algae_18s/algae_18s_seqs.fasta.treefile"))

path_silva_assigns <- here("data/clean/clean_silva_18s_assignments.csv")
silva <- read_csv(path_silva_assigns)

path_field <- here("data/clean/field_clean.csv")
field <- read_csv(path_field)
```

@@

>>>>

```{r, include=F}
rel_abund <- read_csv(here("data/03_filtered/18s_algae/18s_algae.filtered_cleaned_rel_abund.csv"))
algae_taxonomy <- read_csv(here("output/algae_18s_assignments_snow_algae_genbank.csv"))
algae_select_taxonomy <- read_csv(here("output/algae_18s_assignments_w_select_snow_algae.csv"))

tree_18s <- read.tree(here("output/tree/algae_18s/algae_18s_seqs.fasta.treefile"))
field <- read_csv(here("data/02_tidied/tidied_field.csv"))
```

```{r, include=FALSE}
taxonomy <- algae_taxonomy

algae_percent_rel_abund <- rel_abund %>% 
  # calculate rel abund as % of Chlorophyta reads
  group_by(sample_id) %>% 
  mutate(rel_abund = n_reads/sum(n_reads)) %>% 
  ungroup()

best_assignment_rel_abund <- algae_percent_rel_abund %>% 
  # calculate relative abundance per genus
  left_join(taxonomy, by="asv_id") %>% 
  group_by(sample_id, best_assignment) %>% 
  summarise(rel_abund = sum(rel_abund)) %>% 
  ungroup() %>% 
  left_join(field, by="sample_id")

barplot <- ggplot(best_assignment_rel_abund, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=best_assignment), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  labs(title="Assignment with unedited genbank downloads",
       fill = "18S taxonomic assigmnent",
       y="Relative abundance out of Chlorophyta reads",
       x="Sample ID (in order of increasing elevation)")
barplot

# desired categories: lump C nivalis in Chloromonas, lump

```{r}
taxonomy <- algae_select_taxonomy

best_assignment_rel_abund <- algae_percent_rel_abund %>% 
  # calculate relative abundance per genus
  left_join(taxonomy, by="asv_id") %>% 
  group_by(sample_id, best_assignment) %>% 
  summarise(rel_abund = sum(rel_abund)) %>% 
  ungroup() %>% 
  left_join(field, by="sample_id")

barplot_select <- ggplot(best_assignment_rel_abund, aes(x=alias %>% fct_reorder(elev_m), y=rel_abund)) +
  geom_bar(aes(fill=best_assignment), stat="identity") + # classic stacked relative abundance plot
  coord_flip() +
  labs(title="Assignment with select database",
       fill = "18S taxonomic assigmnent",
       y="Relative abundance out of Chlorophyta reads",
       x="Sample ID (in order of increasing elevation)")
barplot_select

Try with consensus sequence for each known snow algae species.

Takehome: 
  - X1.1 has high Trebouxiophyceae of some sort, Koliellaceae
  - W1.1 Chlorogonium (Haematococcaceae), 
  - similar patterns otherwise as rbcL, except no Chlainomonas

```{r}
algae_percent_rel_abund %>% 
  filter(sample_id == "sax18.01") %>% 
  arrange(-rel_abund)
```

top two ASVs in sax18.01 blast as koliellaceae and chloromonas

@@

```{r}
ggsave(here("manuscript/figs/18s_algae_rel_abund.png"), plot = barplot)
```
